---
title: "GEMINI Report"
params:
    rds: !r rds
    dbName: !r dbName
    
output: 
  html_document:
    self_contained: TRUE
    keep_md: TRUE
    df_print: paged
    theme: paper
    highlight: zenburn

---
```{css, echo=FALSE}
.main-container {
  max-width: 1200px;
  margin-left: auto;
  margin-right: auto;
}
```
##   {.tabset}

### **Summary**
```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_total_person(params$dbName, params$rds)
```
The percentage of patients by table based on the total number of patients in the table being compared.
<!--비교 대상이 되는 테이블의 전체 환자 수를 기준으로 한 테이블 별 환자 백분율.-->


```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_total_record(params$dbName, params$rds)
```
The number of records in the table being compared Percentage of records per table based on the sum
<!--비교 대상이 되는 테이블의 레코드 수 총합을 기준으로 한 테이블 별 레코드 백분율. -->

<a href="#Top">TOP</a>

### **Person**
```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName , params$rds, tableName = "person", type = "record")
```
The Percentage of records in the Person table
<!--Person 테이블의 레코드가 차지하는 백분율-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_gender_bar(params$dbName, params$rds)
```
Gender ratio of patients
<!--환자들의 성비-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_visit_freq_graph(params$dbName,params$rds,'min')
```

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_visit_freq_graph(params$dbName,params$rds,'max')
```
The percentage and sex ratio by age, based on the year the patients were first treated and the last year they were treated
<!--환자들이 처음으로 진료받은 연도와 마지막으로 진료받은 연도를 기준으로 한 연령별 백분율 및 성비-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "persontbl_race","race concept id")
```
The percentage of patient race
<!-- 환자 인종별 백분율-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "persontbl_ethnicity", "ethnicity concept id")
```
The percentage of patient ethnicity
<!-- 환자 민족별 백분율 -->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_null_bar(params$dbName, params$rds, "persontbl_location")
```
The number of patients' residential addresses and the percentage of null values
<!-- 환자의 거주 주소의 수 및 Null 값의 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_null_bar(params$dbName, params$rds, "persontbl_provider")
```
The number of people managing patients and the percentage of null values
<!-- 환자를 관리하는 인원 수와 Null 값의 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_null_bar(params$dbName, params$rds, "persontbl_care_site")
```
The number of places that provide medical care to the patient and the percentage of null values
<!-- 환자에게 의료 서비스를 제공하는 장소의 수 및 Null 값의 백분율.-->

<a href="#Top">TOP</a>

***

### **Death**

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "deathtbl_check", "person id")
```
The percentage of deaths recorded by the number of deaths recorded
<!-- 사망자의 사망 날짜가 기록된 개수에 따른 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "deathtbl_type", "death type concept id")
```
The percentage of deaths by type of death
<!-- 사망자의 사망 유형 별 백분율-->

<a href="#Top">TOP</a>

***

### **Visit Occurrence** {.flexbox .vcenter}

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName, params$rds,  tableName = "visit", type = "person")
```
The percentage of records in the Visit Occurrence table
<!-- Visit Occurrence 테이블의 레코드가 차지하는 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName, params$rds, tableName = "visit", type = "record")
```
The percentage of patients in the Visit Occurrence table
<!-- Visit Occurrence 테이블의 환자가 차지하는 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "visittbl_visit_concept", "visit concept id")
```
The percentage by hospital visit concept
<!-- 병원 방문 유형별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_histogram(params$dbName, params$rds, rdsConcept = "visittbl_diff_date")
```
Patient visit duration histogram
<!-- 환자의 방문 기간 히스토그램.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_line_graph(params$dbName, params$rds, rdsConcept = "visittbl_start")
```

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_line_graph(params$dbName, params$rds, rdsConcept = "visittbl_end")
```
The percentage of first visit and last visit to hospital by year
<!-- 연도별 병원 최초 방문 및 마지막 방문 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "visittbl_type_concept", "visit type concept id")
```
The percentage of visit type
<!-- 방문 기록 유형 구분별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_null_bar(params$dbName, params$rds, "visittbl_care_site")
```
The number of types of places where visitors receive medical care and the percentage of null values
<!-- 방문자가 의료 서비스를 받는 장소의 종류 수 및 Null 값의 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "visittbl_source_concept", "visit source concept id")
```
The percentage of visit source
<!-- 방문 구분 코드 별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "visittbl_admitting_source","admitting source concept id")
```
The percentage of visit admitting source
<!-- 방문 허용 코드 별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "visittbl_discharge", "discharge to concept id")
```
The percentage of visit dischage
<!-- 방문 종료 사유별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "visittbl_preceding", "preceding visit occurrence id")
```
The percentage of visits returned per previous visit
<!-- 이전의 방문과 재방문 연관에 따른 비율.-->

<a href="#Top">TOP</a>

***

### **Condition Occurrence** {.flexbox .vcenter}

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName, params$rds, tableName = "condition", type = "person")
```
The percentage of records in the Condition Occurrence table
<!-- Condition Occurrence 테이블의 레코드가 차지하는 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName, params$rds, tableName = "condition", type = "record")
```
The percentage of patients in the Condition Occurrence table
<!-- Condition Occurrence 테이블의 환자가 차지하는 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_histogram(params$dbName, params$rds, rdsConcept = "conditiontbl_diff_date")
```
Patient condition duration histogram
<!-- 질병 기간별 히스토그램.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_line_graph(params$dbName, params$rds, rdsConcept = "conditiontbl_start")
```

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_line_graph(params$dbName, params$rds, rdsConcept = "conditiontbl_end")
```
The percentage by year based on condition identification and termination
<!-- 질병 확인 및 종료에 따른 연도별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "conditiontbl_type_concept", "condition type concept id")
```
The percentage of condition type
<!-- 질병 발생 유형별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_stop_bar(params$dbName, params$rds, "conditiontbl_stop")
```
The number of reasons for stopping condition
<!-- 증상이 나타나지 않게 된 이유의 종류 수. -->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, "conditiontbl_visit_occurrence", "visit detail")
```
The percentage of correlation between condition check and visits
<!-- 증상 확인과 방문 간 상관 관계의 비율.-->

```{r,echo=FALSE, comment= NULL}
draw_pie(params$dbName, params$rds, "conditiontbl_visit_detail", "visit detail")
```
The percentageof correlation between conition and visit
<!-- 증상과 방문 내용과의 상관 관계 비율.-->


<a href="#Top">TOP</a>

***

### **Drug Exposure** {.flexbox .vcenter}

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName, params$rds, tableName = "drug_exp", type = "person")
```
The percentage of patients in the Drug Exposue table
<!-- Drug Exposue 테이블의 환자가 차지하는 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName, params$rds, tableName = "drug_exp", type = "record")
```
The percentage of records in the Drug Exposure table
<!-- Drug Exposue 테이블의 레코드가 차지하는 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_histogram(params$dbName, params$rds, rdsConcept = "drug_exptbl_diff_date")
```
Patient condition duration histogram
<!-- 질병 기간별 히스토그램.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_line_graph(params$dbName, params$rds, rdsConcept = "drug_exptbl_start")
```

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_line_graph(params$dbName, params$rds, rdsConcept = "drug_exptbl_end")
```
The percentage by year based on condition identification and termination
<!-- 질병 확인 및 종료에 따른 연도별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, rdsConcept = "drug_exptbl_type_concept", "drug type concept id")
```
The percentage of drug exposure type
<!-- 약물 제공 유형별 백분율.-->

<!-- NULL -->
```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_stop_bar(params$dbName, params$rds, "drug_exptbl_stop")
```
The number of reasons for stopping drug exposure
<!-- 약물 제공을 중지한 사유의 종류 수. -->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, rdsConcept = "drug_exptbl_route", "route concept id")
```
The percentage of drug exposure route
<!-- 약물 제공을 한 경로별 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_pie(params$dbName, params$rds, rdsConcept = "drug_exptbl_visit_occurrence", "visit occurrence id")
```
The percentage of correlation of drug exposure and visit
<!-- 약물 제공과 방문 간 연관 관계의 비율.-->

<a href="#Top">TOP</a>

***

### **Drug Era** {.flexbox .vcenter}

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName, params$rds, tableName = "drug_era", type = "person")
```
The percentage of records in the Drug Era table
<!-- Drug Era 테이블의 레코드가 차지하는 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_meta_pie(params$dbName, params$rds, tableName = "drug_era", type = "record")
```
The percentage of patients in the Drug Era table
<!-- Drug Era 테이블의 환자가 차지하는 백분율.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_histogram(params$dbName, params$rds, rdsConcept = "drug_eratbl_diff_date")
```
Drug era duration histogram
<!--Drug - 약물 복용 기간에 대한 히스토그램-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_line_graph(params$dbName, params$rds, rdsConcept = "drug_eratbl_start")
```

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_line_graph(params$dbName, params$rds, rdsConcept = "drug_eratbl_end")
```
<!-- This figure shows that the Drug Era start and end.-->

```{r,echo=FALSE, comment= NULL, warning = FALSE}
draw_gap_histogram(params$dbName, params$rds, rdsConcept = "drug_eratbl_gap_days")
```
Histogram of drug delivery day and drug day difference
<!-- 약물 제공일과 약물 복용일 차이에 대한 히스토그램. -->

<a href="#Top">TOP</a>
***
